Blocking-resistant communication\\through domain fronting

### 2014-07-21 docs/meek.tex
Wording.
More abstract tweaking.

\begin{abstract}
We describe ``domain fronting,'' an application-layer technique
for HTTPS
that hides the remote endpoint of a communication
for the purpose of censorship circumvention.
Fronting enables a communication stream that is apparently with an allowed domain,
but actually with a forbidden domain.
The technique uses different domain names at different communication layers.
One domain is used on the ``outside''---in the DNS request and
TLS Server Name Indication---while another is used
on the ``inside''---the HTTP Host header, invisible to the
censor under HTTPS encryption.
A variety of difficult-to-block web services, such as content delivery networks
and Google App Engine, ignore the outside of an HTTPS request
and dispatch it internally according to the Host header:
their frontend servers effectively provide a front,
behind which any domain on their network may be accessed
without revealing the destination to the censor.
If a censor is unable to identify which traffic is fronted,
then blocking the traffic means blocking a content delivery network wholesale,
with resulting expensive collateral damage.
Fronting has been used successfully for a few years by a circumvention system called GoAgent;
we provide a systematic examination of its potential and limitations,
and the results of building an implementation.

We have implemented a system called meek,
a pluggable transport for Tor.
meek combines domain fronting with a simple encoding of a bidirectional byte stream
as HTTPS requests and responses.
A censored client using meek makes a series of HTTPS requests
that appear to be destined to an allowed domain,
but which actually arrive at a special web server on a Tor relay.
The web server decodes the requests, feeds their data into the Tor network,
and sends back any downstream data encoded as HTTPS responses.
We describe our experience deploying meek to Tor users.
meek, or systems inspired by it,
has been adopted by other circumvention systems including Lantern and Psiphon.

>>>>

\begin{abstract}
We describe ``domain fronting,'' an application-layer technique
for HTTPS
that hides the remote endpoint of a communication
for the purpose of censorship circumvention.
Fronting enables a communication stream that is apparently with an allowed domain,
but actually with a forbidden domain.
The technique uses different domain names at different communication layers.
One domain is used on the ``outside''---in the DNS request and
TLS Server Name Indication---while another is used
on the ``inside''---the HTTP Host header, invisible to the
censor under HTTPS encryption.
We identify a number of hard-to-block web services,
like content delivery networks and Google's infrastructure,
that ignore the outside of an HTTPS request
and dispatch it internally according to the Host header.
The effect is that a user may communicate with any domain within the web service,
while appearing to communicate with any other domain.
If a censor is unable otherwise to distinguish fronted and non-fronted traffic,
then blocking circumvention traffic means blocking the whole web service,
with resulting expensive collateral damage.

We have implemented domain fronting in a system called meek,
a pluggable transport for Tor.
meek combines fronting with a proxy server that encodes a TCP stream
as a sequence of HTTP requests and responses.
The meek server's external interface is that of an ordinary web server.
Communication with it is enabled through domain fronting.
The server receives requests, decodes them, and feeds their payloads into a Tor relay,
and returns downstream data in the HTTP response.
A censor watching the communication sees only a sequence of HTTPS requests to an allowed domain.
but which actually arrive at a special web server on a Tor relay.
meek, or something based on it,
has been adopted by other circumvention systems including Lantern and Psiphon.
